# Week 4 Project

## Jhader Aguad

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

```{r}
data(Birthdays, package = "mosaicData")
names(Birthdays)  
```

```{r}
dailyBirths <- Birthdays %>% 
  group_by(date) %>%
  summarise(totalBirths = sum(births))
ggplot(dailyBirths,aes(x=date, y=totalBirths)) + geom_point()
```

#2.a Number if births aggregated over all the years by each week
```{r}
weeklyBirthdays <- Birthdays %>% 
  mutate(WeekDate = week(date)) %>%
  group_by(WeekDate) %>%
  summarise(totalWeekly = sum(births))
ggplot(weeklyBirthdays,aes(x=WeekDate,y=totalWeekly))+geom_point()
```
There are only 52 weeks in a year.

#2.b Number if births aggregated over all the years by each month
```{r}
monthlyBirthdays <- Birthdays %>% 
  mutate(MonthDate = month(date,label=TRUE)) %>%
  group_by(MonthDate) %>%
  summarise(totalMonthly = sum(births))
ggplot(monthlyBirthdays,aes(x=MonthDate, y=totalMonthly))+geom_point()
```
In February there are fewer births because it has fewer days than other months. 


#2.c Number if births aggregated over all the years by each Julian day
```{r}
JulianDayBirthdays <- Birthdays %>% 
  mutate(JulianDayDate = yday(date)) %>%
  group_by(JulianDayDate) %>%
  summarise(totalJulian = sum(births))
ggplot(JulianDayBirthdays,aes(x=JulianDayDate, y=totalJulian))+geom_point()
```
There are only 366 days per year.

#3 Number of birthds by day of the week
```{r}
dayoftheweek <- Birthdays %>% 
  mutate(ByWeekDay = wday(date,label=TRUE)) %>%
  group_by(ByWeekDay) %>%
  summarise(dayoftheweek = sum(births))
ggplot(dayoftheweek,aes(x=ByWeekDay, y=dayoftheweek))+geom_point()
```
In American culture, it is usual for people to schedule a cesarea, and they tend to do it over weekdays. Therefore, fewer babies will be born on the weekends. 

#4 Two-year span
```{r}
MyTwoYears <- Birthdays %>% 
  filter(year(date)%in% 1978:1979) %>%
  group_by(date) %>%
  summarise(births=sum(births))
ggplot(MyTwoYears, aes(x=date, y=births))+geom_point()
```
Cases of birthdays follow the same pattern in two different trends. The upper trend is more dense than the lower trend.
