# Week 6 Project
```{r}

```

## Jhader Aguad

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

First, I download the dataset.
```{r cache=TRUE}
data_site <-"http://tiny.cc/dcf/2014-Q4-Trips-History-Data-Small.rds" 
Trips <- readRDS(gzcon(url(data_site)))
nrow(Trips)
names(Trips)
```
Second, I start with the anaylisis. 
##1
```{r}
Trips %>% ggplot(aes(x=sdate)) + geom_density()
```
More bikes are being rented in October and November than they are in January, because of Winter. 

##2
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) 
         +lubridate::minute(sdate)/60) %>% 
  group_by(time_of_day) %>% 
  ggplot(aes(x=time_of_day)) + geom_density() 
```
Bikes start being rented in the morning and reach their peak at 8am (when people start going to work). There's a small break between 11am and 3pm, but then demand grows again at 4pm-5pm where people return from work. 

##3 & 4
```{r}
Trips %>% 
  mutate(day_of_week = lubridate::wday(sdate)) %>%
  mutate(time_of_day = lubridate::hour(sdate) 
         +lubridate::minute(sdate)/60) %>%
  group_by(time_of_day) %>% 
  ggplot(aes(x=time_of_day)) + geom_density(aes(fill=client),alpha=0.3) + facet_wrap( ~ day_of_week)
```
On Sunday (day=1), casual people tend to use the bicycles more than registered clients in the morning and afterrnon. More registered clients use the bicycles during nightime. During weekdays (day=2,3,4,5,6) we can see a pattern that people that go to work (enter at 8am and leave by 4pm) are more likely to be registered. 
