# Week 3 Project

## Jhader Aguad

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaic)
data("CPS85", package = "mosaicData")
```
<!-- put your content after this line -->

Here is my content!
I replicate the first graph
```{r}
ggplot(data= CPS85, aes(x = exper, y=wage, color=married) ) + geom_point() + facet_wrap(~ sector)
```

I replicate the second graph
```{r}
library(DataComputing)
data(NCHS, package = "DataComputing")
ggplot(data=NCHS, aes(x=bmi)) + geom_density(aes(col=sex)) + facet_wrap(~smoker)
```

Diamonds: color diamonds to be largest on average
```{r}
names(diamonds)
diamonds %>%
  group_by(color) %>%
  summarise(MeanCarat= mean(carat)) %>%
  arrange(desc(MeanCarat)) %>%
  head(1)
```

Diamonds: clarity of diamonds with largest average "table" per carat
```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(MeanTable= mean(table)) %>%
  arrange(desc(MeanTable)) %>%
  head(1)
```

Minneapolis voting: number of cases
```{r}
library(DataComputing)
Minneapolis2013 %>% tally()
```

Minneapolis voting: top 5 candidates
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  tally() %>%
  arrange(desc(n)) %>%
  filter(Second != "undervote") %>%
  head(5)
```

How many undervotes in First choice?
```{r}
library(DataComputing)
Minneapolis2013 %>%
  filter(First == "undervote") %>%
  group_by(First) %>%
  tally()
```

How many undervotes in Second choice?
```{r}
library(DataComputing)
Minneapolis2013 %>%
  filter(Second == "undervote") %>%
  group_by(Second) %>%
  tally()
```

How many undervotes in Third choice?
```{r}
library(DataComputing)
Minneapolis2013 %>%
  filter(Third == "undervote") %>%
  group_by(Third) %>%
  tally()
```

