# Week 2 Short Answer Questions

## Jhader Aguad

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
```
<!-- put your content after this line -->

#1.1 
a) Taffy: value of a variable for a particular case
b) year: quantitative variable
c) sex: categorical variable
d) name: categorical variable
e) count: quantitative variable

#1.2
1) president's values are not consistent in format (Last Name, Firts Name) and (First Name Last Name) and there are ilegal punctutations (,).
2) in office values are also inconsistent (sometimes uses "-" and "to")
3) it depends is not a numerical value

#1.4
1. Table A: "Year," "Algeria," "Brazil," "Columbia"
   Table B: "Country," "Y2000," "Y2001"
   Table C: "Country," "Year," "Value"
   
2. Table A: a year
   Table B: a country
   Table C: a country in a year
 
#2.2
"File name"

#2.3
```{r}
library("mosaicData")
data(CPS85, package="mosaicData")
```


#2.4
Wrong because it is naming an object with the command <- as opposed to ask for NHANES

#2.6
first-essay has problem with illegal punctuation
"MyData" has illegal punctuation
small sample has a space 
sqrt() stands for square root and it's already a function

#2.7
data(flights, package = "nycflights13")
help(flights)
View(flights)
ncol(flights)
nrow(flights)

1. 19 variables
2. 336776
3. flight number
5. air_time = minutes
   distance = miles
   
#2.8
a. improper syntax for function argument
b. No mistake
c. invalid objext name
d. Unmatched quotes
e. no assigmnent operator

#2.9
. and _ can be used
all of them

#3.1
fireplace %>%
fireplace()
Hello(fireplace)
Hola$fireplace

#3.2
Either you assing or chain:
It will work if Results is a Data_Table
Result %>% filter(BabyNames, name=="Prince")

#3.3
<- is the assignment operator

#4.2
```{r}
9+7
```



